---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# didintrjl

<!-- badges: start -->
[![R-CMD-check](https://github.com/ebjamieson97/didintrjl/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ebjamieson97/didintrjl/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/didintrjl)](https://CRAN.R-project.org/package=didintrjl)
[![Codecov test coverage](https://codecov.io/gh/ebjamieson97/didintrjl/graph/badge.svg)](https://app.codecov.io/gh/ebjamieson97/didintrjl)
<!-- badges: end -->

## Overview

**didintrjl** is an R wrapper for the Julia package [DiDInt.jl](https://ebjamieson97.github.io/DiDInt.jl/dev/), which implements intersection difference-in-differences (DID-INT),
a method developed by [Karim & Webb (2025)](https://arxiv.org/abs/2412.14447). DID-INT allows for unbiased estimation of the average effect of treatment on the treated
(ATT) in cases when the common causal covariates (CCC) assumption is violated.

## Installation

You can install the development version of didintrjl with:
``` r
# install.packages("remotes")
remotes::install_github("ebjamieson97/didintrjl")
```

## Examples

The `didint()` function returns an object with the class `DiDIntObj` which has three S3 methods: `print()`, `summary()`, and `coef()`. Each of these methods
have the argument `level` which can take either `"agg"` or `"sub"` in order to distinguish between aggregate results and sub-aggregate results. For example,
in a staggered adoption setting with several different treatment times, setting `level = "sub"` will return information pertinent to the distinct treatment times, whereas
`level = "agg"` would return the aggregated results.

```{r}
# Load data
df <- read.csv("inst/extdata/merit.csv")

# Load didintrjl and run didint()
library(didintrjl)
res <- didint("coll", "state", "year", df, verbose = FALSE,
              treated_states = c(71, 58, 64, 59, 85, 57, 72, 61, 34, 88),
              treatment_times = c(1991, 1993, 1996, 1997, 1997, 1998, 1998, 1999, 2000, 2000))

# Print aggregate and then sub-aggregate results
summary(res)
summary(res, level = "sub")
```

